---
title: "Biking trends"
subtitle: "In this document I present my biking trends"
author: "Krzysztof Nowak"
email: knowak1990@outlook.com
date: today
description: ""
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    toc: true
    toc-location: left
    title-block-banner: "lightgray"
    
title-block-banner-color: "black"
number-sections: true
editor: visual
---

# Introduction

I recently got back into cycling and decided to keep statistics on the distance and duration of my trips.

# Load libraries and custom functions

I work with tidyverse library for most of data manipulation and patchwork to control a way in which charts are presented

```{r, warning=FALSE, message=FALSE,echo=FALSE}
# Library
library(tidyverse)
library(patchwork)
library(plotly)
#load custom functions library
source("bikefunctions.R")

```

```{r, warning=FALSE, message=FALSE,echo=FALSE}
#Laod data
DF <- readRDS('Biking.rds')

MaxDistance <- which.max(DF$Distance)

DFText <- DF |>
  mutate(text = case_when(Index == MaxDistance ~  "Katowice trip", TRUE ~ NA))



```

```{r, warning=FALSE, message=FALSE,echo=FALSE}

TitleDuration <- 'Time spend on bike'
TitleDistance <- 'Kilometers traveled by bike'
TitleKilometershour <- 'Kilometers per hour'

```

::: {.callout-note collapse="true"}
## Note on custom functions

Please be advised that definition of custom function is available in *bikingfunctions.R* file within this repository
:::

```{r}

p1 <- ChartLineTemplate(Data = DFText,
                        xA = "Date",
                        yA = "Duration",
                        title = TitleDuration,
                        Units = "Minutes")

p2 <- ChartLineTemplate(Data = DFText,
                  xA = "Date",
                  yA = "Distance",
                  title = TitleDistance,
                  Units = "Kilometers") 

(p1/p2)
```

```         
```
